DraftOne

### 2016-07-05 writing/JSSDraft/JSSDraft.Rmd
Copyediting

For many environmental time series studies, including those investigating air pollution and temperature, both exposures and outcomes can have complex seasonal and longer-term patterns over the study period. For example, air pollution concentrations can change seasonally, both because of changes in emission patterns and meteorological patterns (for example, winter inversion layers can cause a build-up of particulate matter in the winter, while high temperatures in the summer can accelate ozone formation from precursors); air pollution concentrations can also change over years, especially with evolving Clean Air policies.

@@

There are a few important advantages to having an open-source software package that can simulate this type of environmental time series for simulation studies. First, current methods of simulating environmental time series, to use to assess modeling choices, vary across different studies. While, ideally, results from a simulation study would be robust to different choices in how to simulate the data used in the study, this may not always be the case; if so, results across studies using different methods of simulating data would not be comparable \citep{Alfons2010}. This package offers a tool that both allows different research to simulate environmental time series for simulation studies in a consistent way, it also offers several methods of simulating time series, and so allows researchers to check if simulation results are sensitive to the method of simulating study data. Tools for consistency across studies have helped in the progress of environmental epidemiology research; for example, the public availability of the NMMAPs dataset--which included air pollution, weather, and mortality counts in over 100 US communities for 14 years-- allowed researchers around the world to explore hypotheses and investigate health effects of air pollution and temperature using the same data, and so differences in results could be traced to methodological differences rather than random differences in environmental datasets. [We could add some on the usefulness of (1) reproducible studies and (2) open source software for scientific studies here.]

Further, developing the code to simulate environmental time series in an appropriate way can be time consuming. While researchers often need to customize certain parts of a simulation, to test a particular research question, often most of the simulation can be performed in a way that is generalizable across most other environmental time series studies. Therefore, by providing simulation tools with reasonable defaults, as well as room to customize at each step of the simulation, this package can make environmental epidemiolgoy simulation studies much more efficient and also make simulation a reasonable alternative for determining expected power when planning and proposing future studies.

@@

\citet{Armstrong2014} used a simulation study to investigate whether evidence of short-term mortality displacement following heat waves was a result of model artifacts. To do this, they aimed to simulate a time series of heat wave (binary) effects with heat wave effects, none of which were caused by short-term mortality displacement. They then showed that, when they fit the model from the previous study to this simulated dataset, the model generated results suggestive of short-term mortality displacement, and less displacement with more severe heat waves than less severe heat waves, which were similar to the findings of the study they were assessing. Overall, this analysis suggested that the earlier study's results might have been an artifact of the modeling approach they used, and so their results could be consistent with a hypothesis of no mortality displacement.

>>>>

For many environmental time series studies, including those investigating air pollution and temperature, both exposures and outcomes can have complex seasonal and longer-term patterns over the study period. For example, air pollution concentrations can change seasonally, both because of changes in emission patterns and meteorological patterns (for example, winter inversion layers can cause a build-up of particulate matter in the winter, while high temperatures in the summer can accelerate ozone formation from precursors); air pollution concentrations can also change over years, especially with evolving Clean Air policies.

@@

There are a few important advantages to having an open-source software package that can simulate this type of environmental time series for simulation studies. First, current methods of simulating environmental time series to use to assess modeling choices vary across different studies. While, ideally, results from a simulation study would be robust to different choices in how to simulate the data used in the study, this may not always be the case; if so, results across studies using different methods of simulating data would not be comparable \citep{Alfons2010}. This package offers a tool that both allows different research to simulate environmental time series for simulation studies in a consistent way, it also offers several methods of simulating time series, and so allows researchers to check if simulation results are sensitive to the method of simulating study data. Tools for consistency across studies have helped in the progress of environmental epidemiology research; for example, the public availability of the NMMAPs dataset--which included air pollution, weather, and mortality counts in over 100 US communities for 14 years-- allowed researchers around the world to explore hypotheses and investigate health effects of air pollution and temperature using the same data, and so differences in results could be traced to methodological differences rather than random differences in environmental datasets. [We could add some on the usefulness of (1) reproducible studies and (2) open source software for scientific studies here.]

Further, developing the code to simulate environmental time series in an appropriate way can be time consuming. While researchers often need to customize certain parts of a simulation, to test a particular research question, often most of the simulation can be performed in a way that is generalizable across most other environmental time series studies. Therefore, by providing simulation tools with reasonable defaults, as well as room to customize at each step of the simulation, this package can make environmental epidemiology simulation studies much more efficient and also make simulation a reasonable alternative for determining expected power when planning and proposing future studies.

@@

\citet{Armstrong2014} used a simulation study to investigate whether evidence of short-term mortality displacement following heat waves was a result of model artifacts. To do this, they aimed to simulate a time series of heat wave (binary) effects with heat wave effects, none of which were caused by short-term mortality displacement. They then showed that when they fit the model from the previous study to this simulated dataset, the model generated results suggestive of short-term mortality displacement, and less displacement with more severe heat waves than less severe heat waves, which were similar to the findings of the study they were assessing. Overall, this analysis suggested that the earlier study's results might have been an artifact of the modeling approach they used, and so their results could be consistent with a hypothesis of no mortality displacement.
